---
title: "607_assignment_9"
output: html_document
date: "2023-03-20"
---

The purpose of the assignment is to choose one of the New York Times APIs, construct an interface in R to read in the JSON data, and
transform it into an R DataFrame.

## Load Package
```{r}
library(tidyverse)
library(httr)
library(jsonlite)
```

## Pulling the API
The NYT API will be focusing on the graphic books and manga published by VIZ media, a famous publisher known for japanese manga, and see how many books are in the top-selling list.

```{r}
#set up base and other paths for API
api_base <- "https://api.nytimes.com/svc/books/v3"
api_book <- "/lists/current/graphic-books-and-manga"
api_key <- ".json?api-key="
my_key <- read.delim("nyt_api_key.txt", header = FALSE) #the API is stored locally
api_url <- paste0(api_base, api_book, api_key, my_key)

# extract data from api link
raw_api_data <- GET(api_url)

# check status of the API
http_status(raw_api_data)
```

## Turn raw JSON into a dataframe
```{r}
#convert json to dataframe
json_book_data <- fromJSON(rawToChar(raw_api_data$content))
book_data <- as.data.frame(json_book_data$results$books)

knitr::kable(book_data)
```

## View only books from the publisher, VIZ media
```{r}
viz_book_data <- subset(book_data, book_data$publisher == 'VIZ Media', select = c("rank", "publisher", "title", "author", "description"))

knitr::kable(viz_book_data)
```

## Conclusion
In conclusion, APIs can be useful tools in extracting raw json data effectively.
